---
title: "Calculating effect sizes (Cohen's d) for systematic review on semantic fluency and amyloid"
output: html_notebook
Authors: Emma Twait & Jet Vonk
Date (last updated): June 24 2020 
---

## NOTE: FIRST GROUP IS ALWAYS AMYLOID NEGATIVE

## install esc package
## Lüdecke, Daniel. 2018. Effect Size Computation for Meta Analysis. 
## https://CRAN.R-project.org/package=esc.
install.packages("esc")

```{r}
library(esc)
```


###This is the adjusted function from the esc_beta code to calculate effect size for standardized regression coefficients with a continuous predictor (adjusted by Jet Vonk)
```{r}
#' @param beta The standardized beta coefficient.
#' @param sdy The standard deviation of the dependent variable.
#' @param totaln Total group sample size.
#' @param es.type Type of effect size that should be returned.

# Compute variance of d-type effect size
esc.vd_tot <- function(d, totaln) {
  (totaln) / (grp1n * grp2n) + (d * d) / (2 * (grp1n + grp2n))
}

# 95% confidence interval
#' @importFrom stats qnorm
lower_d <- function(d, v) d - stats::qnorm(.975) * sqrt(v)
upper_d <- function(d, v) d + stats::qnorm(.975) * sqrt(v)


esc_beta_cont <- function(beta, sdy, totaln,
                     es.type = c("d", "g", "or", "logit", "r", "f", "eta", "cox.or", "cox.log"),
                     study = NULL) {
  # match  arguments
  es.type <- match.arg(es.type)

  b <- beta 

  es <- b / sdy
  v <- esc.vd(es, grp1n, grp2n)

  # return effect size
  esc_generic(
    es = es,
    v = v,
    es.type = es.type,
    grp1n = grp1n,
    grp2n = grp2n,
    info = "standardized regression coefficient",
    study = study
  )
}
```



## Verfaillie (2019)
## 63 (AB-=44, AB+=19)
## picture naming
## mean, sd
## AB-=79.1 (10.3), AB+= 82.0 (3.3)
## semantic fluency
## mean, sd
## AB-=24.2 (5.7), AB+=23.6 (4.7)
```{r}
Verfaillie_PN <- esc_mean_sd(grp1m = 79.1, grp1sd = 10.3, grp1n = 44,
            grp2m = 82.0, grp2sd = 3.3, grp2n = 19, es.type = "d")
Verfaillie_SF <- esc_mean_sd(grp1m = 24.2, grp1sd = 5.7, grp1n = 44,
            grp2m = 23.6, grp2sd = 4.7, grp2n = 19, es.type = "d")
Verfaillie_PN
Verfaillie_SF
```


## Verberk (2020)
## 241
## picture naming
## standardized beta ± SE
## -0.15 ± 0.08 (SDy = 0.2)
## semantic fluency
## standardized beta ± SE
## 0.03 ± 0.06 (SDy = 6)
```{r}
Verberk_PN <- -0.15/.2
Verberk_SF <- 0.03/6
Verberk_PN 
Verberk_SF
```

  
## Mielke (2016)
## AB+=81, AB-=383
## picture naming
## b (SE)
##-0.16 (0.24)
## SE -> SD
## 0.24*sqrt(464)
## b (SD)
## -0.16 (5.20)
## mean, sd
## AB+=56.4 (3.3), AB-=56.6 (3.3)
## semantic fluency
## b (SE)
## 0.05 (0.22)
## SE -> SD
## 0.05*sqrt(464)
## b (SD)
## 0.05 (1.08)
## mean, sd
## AB+=49.1 (9.9), AB-=49.8 (10.1)

Mielke_PN_b <- esc_beta(beta=-0.16, sdy=5.20, grp1n=383, grp2n=81, es.type = "d")
Mielke_SF_b <-esc_beta(beta=-0.05, sdy=1.08, grp1n=383, grp2n=81, es.type = "d")

```{r}
Mielke_PN_c <-esc_mean_sd(grp1m = 56.6, grp1sd = 3.3, grp1n = 383,
                          grp2m = 56.4, grp2sd = 3.3, grp2n = 81, es.type = "d")
Mielke_SF_c <- esc_mean_sd(grp1m = 49.8, grp1sd = 10.1, grp1n = 383,
                           grp2m = 49.1, grp2sd = 9.9, grp2n = 81, es.type = "d")
Mielke_PN_c
Mielke_SF_c
```
                    

## Hassentab (2016)
## 264 (TOTAL AB-=177,AB+=87; 65-74 AB-=127, AB+=53; 75+ AB-=50, AB+=34)
## picture naming
## 65-74
## mean, sd
## AB-= 55.88 (4.25), AB+= 56.58 (4.17)
## 75+
## mean, sd
## AB-=53.88 (5.21), AB+=51.59 (6.38)
## semantic fluency
## 65-74
## mean, sd
## ANIMALS AB-=21.14 (5.15), AB+=21.82(4.83); VEGETABLES AB-=15.05 (4.16), AB+=14.97 (4.50)
## 75+
## ANIMALS AB-=18.31 (4.71), AB+=16.91 (3.87); VEGETABLES AB-=14.14 (4.08), AB+=11.96 (4.03)

Hassentab_PN_young <- esc_mean_sd(grp1m = 55.88, grp1sd = 4.25, grp1n = 127,
                                  grp2m = 56.58, grp2sd = 4.17, grp2n = 53, es.type = "d")
Hassentab_PN_old <-esc_mean_sd(grp1m = 53.88, grp1sd = 5.21, grp1n = 50,
                               grp2m = 51.59, grp2sd = 6.38, grp2n = 34, es.type = "d")
Hassentab_SF_young_animals <- esc_mean_sd(grp1m = 21.14, grp1sd = 5.15, grp1n = 127,
                                          grp2m = 21.82, grp2sd = 4.83, grp2n = 53, es.type = "d")
Hassentab_SF_young_vegetables <- esc_mean_sd(grp1m = 15.05, grp1sd = 4.16, grp1n = 127,
                                            grp2m = 14.97, grp2sd = 4.50, grp2n = 53, es.type = "d")
Hassentab_SF_old_animals <- esc_mean_sd(grp1m = 18.31, grp1sd = 4.71, grp1n = 50,
                                        grp2m = 16.91, grp2sd = 3.87, grp2n = 34, es.type = "d")
Hassentab_SF_old_vegetables <- esc_mean_sd(grp1m = 14.14, grp1sd = 4.08, grp1n = 50,
                                          grp2m = 11.96, grp2sd = 4.03, grp2n = 34, es.type = "d")

## Li (2007)
## 72 (AB-=51, AB+=21)
## semantic fluency
## mean, sd
## AB-=23 (6); AB+=20 (5)

```{r}
Li_SF <- esc_mean_sd(grp1m = 23, grp1sd = 6, grp1n = 51,
                     grp2m = 20, grp2sd = 5, grp2n = 21, es.type = "d")
Li_SF
```



## Edmonds (2015)
## 570 (stage 0 = 142, stage 1 = 48, stage 2 = 173, stage 3 = 50, SNAP = 138; 
## 0 markers=142, 1 marker=190, 2 markers=188, 3 markers=50)
## picture naming
## mean, sd STAGE 0
## 28.0 (1.8)
## mean, sd STAGE 1
## 28.2 (1.7)
## mean, sd STAGE 2
## 27.8 (2.3)
## mean, sd STAGE 3
## 26.4 (2.6)
## mean, sd SNAP
## 28.1 (2.2)
## mean, sd 0 markers
## 28.0 (1.8)
## mean, sd 1 marker
## 28.2 (1.9)
## mean, sd 2 markers
## 27.6 (2.4)
## mean, sd 3 markers
## 26.4 (2.6)

## Payoux (2015)
## 271 (AB-=158, AB+=77)
## semantic fluency
## mean, sd
## AB-=26.87 (7.12), AB+=25.23 (6.51)

```{r}
Payoux_SF <- esc_mean_sd(grp1m = 26.87, grp1sd = 7.12, grp1n = 158,
                         grp2m = 25.23, grp2sd = 6.51, grp2n = 77, es.type = "d")
Payoux_SF
```



## Um (2016)
## 50 (AB-=34, AB+= 16)
## picture naming
## mean, sd
## AB-=11.1 (3.1), AB+= 12.1 (2.3)
## semantic fluency
## mean, sd
## AB-=14.3 (2.7), AB+= 13.7 (3.2)

```{r}
Um_PN <- esc_mean_sd(grp1m = 11.1, grp1sd = 3.1, grp1n = 34,
                     grp2m = 12.1, grp2sd = 2.3, grp2n = 16, es.type = "d")
Um_SF <- esc_mean_sd(grp1m = 14.3, grp1sd = 2.7, grp1n = 34,
                     grp2m = 13.7, grp2sd = 3.2, grp2n = 16, es.type = "d")
Um_PN
Um_SF
```



## Papp (2017)
## 279 (AB+=70, AB-=209)
## semantic fluency
## mean, sd
## category only AB+= 44.93 (9.97), AB-= 44.24 (10.02)
##ANIMALS AB+= 18.19 (4.50), AB-=17.73 (5.25)

```{r}
Papp_SF <- esc_mean_sd(grp1m = 17.73, grp1sd = 5.25, grp1n = 209,
                       grp2m = 18.19, grp2sd = 4.50, grp2n = 70, es.type = "d")
Papp_SF
```



## Amariglio (2012)
## 131 AB-= 97, AB+= 34
## picture naming
## mean, sd
## AB-=28.3 (2), AB+= 27.8 (1.6)

```{r}
Amariglio_PN <- esc_mean_sd(grp1m = 28.3, grp1sd = 2.0, grp1n = 97,
                            grp2m = 27.8, grp2sd = 1.6, grp2n = 34, es.type = "d")
Amariglio_PN
```



## Lim (2013c)
## 178 (AB-= 123, AB+= 55)
## picture naming
## mean, sd
## AB-= 28.06 (2.76), AB+= 28.33 (2.70)
## semantic fluency
## mean, sd
## AB-= 38.30 (8.33), AB+= 39.60 (8.27)

```{r}
Lim_PN <- esc_mean_sd(grp1m = 28.06, grp1sd = 2.76, grp1n = 123,
                      grp2m = 28.33, grp2sd = 2.70, grp2n = 55, es.type = "d")
Lim_PN
```


Lim_SF <- esc_mean_sd(grp1m = 38.30, grp1sd = 8.33, grp1n = 123,
                      grp2m = 39.60, grp2sd = 8.27, grp2n = 55, es.type = "d")

## Doraiswamy (2014)
## 67 (AB+= 10, AB-=57)
## semantic fluency
## mean, sd
## ANIMALS AB+=18.30 (4.45), AB-=20.00 (4.24) VEGETABLES AB+=13.10 (3.21), AB-=14.02 (3.51)

```{r}
Doraiswamy_SF_animals <- esc_mean_sd(grp1m = 20.00, grp1sd = 4.24, grp1n = 57,
                                     grp2m = 18.30, grp2sd = 4.45, grp2n = 10, es.type = "d")
Doraiswamy_SF_animals
```


Doraiswamy_SF_vegetables <- esc_mean_sd(grp1m = 14.02, grp1sd = 3.51, grp1n = 57,
                                     grp2m = 13.10, grp2sd = 3.21, grp2n = 10, es.type = "d")

## Dubois (2018)
## 318 A+= 88, A-= 230
## picture naming
## mean, sd
## AB+=79.22 (1.08), AB-=79.20 (1.12)
## semantic fluency
## mean, sd
## A+= 30.60 (6.10), AB-= 31.60 (7.44)

```{r}
Dubois_PN <- esc_mean_sd(grp1m = 79.20, grp1sd = 1.12, grp1n = 230,
                         grp2m = 79.22, grp2sd = 1.08, grp2n = 88, es.type = "d")
Dubois_SF <- esc_mean_sd(grp1m = 31.60, grp1sd = 7.44, grp1n = 230,
                         grp2m = 30.60, grp2sd = 6.10, grp2n = 88, es.type = "d")
Dubois_PN
Dubois_SF
```




## Price (2009)
## 97 (AB-=59, AB+=38)
## picture naming
## mean, SE
## AB-=54.0, 0.9; AB+= 54.1, 1.1
## limbic plaque r, N
## -0.07, 38
## neocorex plaque r, N
## -0.01, 36
## limbic SPs r, N
## -0.02, 30
## neocortex SPs r, N
## 0.11, 31
## semantic fluency
## mean, SE
## AB-= 16.7, 0.9; AB+= 15.5, 1.2
## limbic plaque r, N
## 0.12, 42
## neocorex plaque r, N
## 0.21, 39
## limbic SPs r, N
## 0.23, 32
## neocortex SPs r, N
## 0.25, 35


```{r}
Price_PN_cat <- esc_mean_se(grp1m = 54.0, grp1se = 0.9, grp1n = 59,
                        grp2m = 54.1, grp2se = 1.1, grp2n = 38, es.type = "d")
Price_SF_cat <- esc_mean_se(grp1m = 16.7, grp1se = 0.9, grp1n = 59,
                        grp2m = 15.5, grp2se = 1.2, grp2n = 38, es.type = "d")
Price_PN_cat
Price_SF_cat
```


Price_PN_LP <- esc_rpb(r = -0.07, totaln = 38, es.type = "d")
Price_PN_NP <- esc_rpb(r = -0.01, totaln = 36, es.type = "d")
Price_PN_LS <- esc_rpb(r = -0.02, totaln = 30, es.type = "d")
Price_PN_NS <- esc_rpb(r = 0.11, totaln = 31, es.type = "d")
Price_SF_LP <- esc_rpb(r = 0.12, totaln = 42, es.type = "d")
Price_SF_NP <- esc_rpb(r = 0.21, totaln = 39, es.type = "d")
Price_SF_LS <- esc_rpb(r = 0.23, totaln = 32, es.type = "d")
Price_SF_NS <- esc_rpb(r = 0.25, totaln = 35, es.type = "d")

## Sperling (2013)
## 78 (AB+=11, AB-=67 VISUAL; AB+=18, AB-=60 SUVR)
## semantic fluency
## r VEGETABLES, SUVr
## 0.002
## r ANIMALS
## 0.017
## mean, SE, SUVR
## VEGETABLES AB-=14.0 (0.4), AB+=13.8 (1.0) mean, SE ANIMALS AB-=20.2 (0.5), AB+=19.1 (1.5)
## mean, SE, visual
## VEGETABLES AB-=13.9 (0.4), AB+=14.2 (1.4), ANIMALS AB-=19.9 (0.5), AB+=20.1 (2.2)

```{r}
Sperling_SF_r_animals <- esc_rpb(r = 0.017, grp1n = 60, grp2n = 18, es.type = "d")
Sperling_SF_SUVR_animals <- esc_mean_se(grp1m = 20.2, grp1se = 0.5, grp1n = 60,
                                        grp2m = 19.1, grp2se = 1.5, grp2n = 18, es.type = "d")
Sperling_SF_r_animals
Sperling_SF_SUVR_animals
```



## Snitz (2020)
## 118 (AB-=84, AB+=34)
## semantic fluency
## standardized estimate, 95% CI global
## 0.07 (-0.25, 0.11)

## Sala Llonch (2015)
## 89 (AB-=62, AB+27)
## semantic fluency
## mean, sd, range
## AB-=20.69 (5.22) (10-32), AB+=20.63 (6.04) (5-30)

```{r}
SalaLlonch_SF <- esc_mean_sd(grp1m = 20.69, grp1sd = 5.22, grp1n = 62,
                             grp2m = 20.63, grp2sd = 6.04, grp2n = 27, es.type = "d")
SalaLlonch_SF
```



## Oh (2011)
## 52 AB-=33, AB+=19
## picture naming
## mean, sd
## AB-= 14.79 (0.41), AB+= 14.47 (0.90)


```{r}
Oh_2011_PN <- esc_mean_sd(grp1m = 14.79, grp1sd = 0.41, grp1n = 33,
                          grp2m = 14.47, grp2sd = 0.90, grp2n = 19, es.type = "d")
Oh_2011_PN 
```
                          

## Oh (2012)
## 189 (AB-= 34, AB+= 18)
## semantic fluency
## mean, range, SD
## AB-=15.84 (6-30) 5.04; AB+= 16.41 (6-26) 4.96 VEGETABLES AB-=20.00 (7-31) 4.97; AB+= 22.35 (10-46) 7.69 ANIMALS

```{r}
Oh_2012_SF_vegetables <- esc_mean_sd(grp1m = 15.84, grp1sd = 5.04, grp1n = 34,
                                     grp2m = 16.41, grp2sd = 4.96, grp2n = 18, es.type = "d")
Oh_2012_SF_animals <- esc_mean_sd(grp1m = 20.00, grp1sd = 4.97, grp1n = 34,
                                  grp2m = 22.35, grp2sd = 7.69, grp2n = 18, es.type = "d")
Oh_2012_SF_animals
```



## Lee (2020)
## 97 (AB+=63, AB-=34)
## picture naming
## r
## 0.23

```{r}
Lee_PN <- esc_rpb(r = 0.023, grp1n = 34, grp2n = 63, es.type = "d")
Lee_PN
```


#Harrington
#categorical: Harrington_SF <- esc_mean_sd(grp1m = 43.47, grp1sd = 8.70, grp1n = 277,
#                                    grp2m = 41.09, grp2sd = 10.81, grp2n = 58, es.type = "d")
                                    
```{r}
Harrington_SF <- esc_f(f=3.07,grp1n = 277,grp2n = 58,es.type = "d")
Harrington_SF
```

#Mathis
#SF: AB-=15.9 (3.6), AB+=15.4 (3.6)
#152 (AB-=74, AB+=78)
```{r}
Mathis_SF <- esc_mean_sd(grp1m = 15.9, grp1sd = 3.6, grp1n = 74,
                                     grp2m = 15.4, grp2sd =3.6, grp2n = 78, es.type = "d")
Mathis_SF
```

#Bennett
#PN:AB-=14.0 (1.1); AB+=13.5 (1.2)
#SF:AB-=32.4 (8.1); AB+=29.3 (7.9)
#134 (AB-=84, AB+=50)
```{r}
Bennett_PN <- esc_mean_sd(grp1m = 14, grp1sd = 1.1, grp1n = 84,
                                     grp2m = 13.5, grp2sd = 1.2, grp2n = 50, es.type = "d")
Bennett_PN

Bennett_SF <- esc_mean_sd(grp1m = 32.4, grp1sd = 8.1, grp1n = 84,
                                     grp2m = 29.3, grp2sd = 7.9, grp2n = 50, es.type = "d")
Bennett_SF
```

#Bos
#SF:AB-= 21.6 (5.7), AB+=20.9 (5.5)
#(AB-=526, AB+=190)
```{r}
Bos_SF <- esc_mean_sd(grp1m = 21.6, grp1sd = 5.7, grp1n = 526,
                                     grp2m = 20.9, grp2sd = 5.5, grp2n = 190, es.type = "d")
Bos_SF
```


###########Cochrane formula combining two groups
```{r}
Calc2 <- function(n1,m1,sd1,n2,m2,sd2) # n mean and SD of two groups
{
  out<-cat("grp1"," n=",n1," mean=",m1," SD=", sd1, "\n")
  out<-cat("grp2"," n=",n2," mean=",m2," SD=", sd2, "\n")
  tn = n1 + n2
  tmean = (n1*m1 + n2*m2) / (n1 + n2)
  tsd = sqrt(((n1-1)*sd1^2 + (n2-1)*sd2^2 + n1 * n2 / (n1 + n2) * (m1^2 + m2^2 - 2 * m1 * m2)) / (n1 + n2 -1))
  out<-cat("grp1+2"," n=",tn," mean=",tmean," SD=", tsd, "\n")
  c(tn, tmean, tsd)
}

#example
#ar <- Calc2(g1[1],g1[2],g1[3],g2[1],g2[2],g2[3]) # combine group 1+2
#ar <- Calc2(ar[1],ar[2],ar[3],g3[1],g3[2],g3[3]) # add grp 3 to result of combined 1+2
```


#Clark
```{r}
ABneg <- Calc2(215,24.2,.5,25,23.3,1.2) # combine group 1+3
ABpos <- Calc2(46,23.9,.8,28,22.4,1.2) # combine group 2+4
```

#ABneg: n= 240  mean= 24.10625  SD= 0.6665989 
#ABpos: n= 74  mean= 23.33243  SD= 1.20979 
```{r}
Clark_SF <- esc_mean_sd(grp1m = 24.10625, grp1sd = 0.6665989, grp1n = 240,
                           grp2m = 23.33243, grp2sd = 1.20979, grp2n = 74, es.type = "d")
Clark_SF
```

#Edmonds

#PICTURE NAMING
#stage 0: 28.0 (1.8) n=142
#st.SNAP: 28.1 (2.2) n=138
#stage 1: 28.2 (1.7) n=48
#stage 2: 27.8 (2.3) n=173
#stage 3: 26.4 (2.6) n=50
```{r}
ABneg <- Calc2(142,28,1.8,138,28.1,2.2) # combine group 0+SNAP

#ABpos1 <- Calc2(48,28.2,1.7,173,27.8,2.3) # combine group 1+2
ABpostot <- Calc2(221,27.88688,2.186448,50,26.4,2.6) # combine group 1+2 + 3
```
#ABneg: n= 280  mean= 28.04929  SD= 2.004135 
#ABpos: n= 271  mean= 27.61255  SD= 2.335798 
```{r}
Edmonds_PN <- esc_mean_sd(grp1m = 28.04929, grp1sd = 2.004135, grp1n = 280,
                           grp2m = 27.61255, grp2sd = 2.335798, grp2n = 271, es.type = "d")
Edmonds_PN
```

#SEMANTIC FLUENCY
#mean, sd STAGE 0:  20.3 (5.0) 142
#mean, sd SNAP	 :  20.9 (5.1) 138
#mean, sd STAGE 1:	20.4 (5.3) 48
#mean, sd STAGE 2:	20.2 (4.7) 173
#mean, sd STAGE 3:	16.1 (3.9) 50
```{r}
ABneg <- Calc2(142,20.3,5.0,138,20.9,5.1) # combine group 0+SNAP

#ABpos1 <- Calc2(48,20.4,5.3,173,20.2,4.7) # combine group 1+2
ABpostot <- Calc2(221,20.24344,4.824753,50,16.1,3.9) # combine group 1+2 + 3
```
#ABneg: n= 280  mean= 20.59571  SD= 5.049421  
#ABpos: n= 271  mean= 19.47897  SD= 4.93158 
```{r}
Edmonds_SF <- esc_mean_sd(grp1m = 20.59571, grp1sd = 5.049421, grp1n = 280,
                           grp2m = 19.47897, grp2sd = 4.93158, grp2n = 271, es.type = "d")
Edmonds_SF
```


#Jicha
#mean, sd stage 0	16.4 (5.5) 59
#mean, sd stage 0-N	16.6 (4.4) 13
#mean, sd stage 1	16.2 (5.2) 13
#mean, sd stage 2	14.4 (4.4) 15
#mean, sd stage 3	15.9 (4.5) 26
```{r}
ABneg <- Calc2(59,16.4,5.5,13,16.6,4.4) # combine group 0+SNAP

#ABpos1 <- Calc2(13,16.2,5.2,15,14.4,4.4) # combine group 1+2
ABpostot <- Calc2(28,15.23571,4.78456,26,15.9,4.5) # combine group 1+2 + 3
```
#ABneg  n= 72  mean= 16.43611  SD= 5.290499 
#ABpos  n= 54  mean= 15.55555  SD= 4.618019 
```{r}
Jicha_SF <- esc_mean_sd(grp1m = 16.43611, grp1sd = 5.290499, grp1n = 72,
                           grp2m = 15.55555, grp2sd = 4.618019, grp2n = 54, es.type = "d")
Jicha_SF
```

#Soldan
#% correct mean, SD (stage 0)	96.1 (5.9) 102
#% correct mean, SD (SNAP)	95.1 (6.5) 46 
#% correct mean, SD (stage 1)	96.4 (5.7) 46
#% correct mean, SD (stage 2)	94.8 (6.0) 28
```{r}
ABneg <- Calc2(102,96.1,5.9,46,95.1,6.5) # combine group 0+SNAP

ABpos <- Calc2(46,96.4,5.7,28,94.8,6.0) # combine group 1+2
```
#ABneg n= 148  mean= 95.78919  SD= 6.088219 
#ABpos  n= 74  mean= 95.79459  SD= 5.826966 
```{r}
Soldan_PN <- esc_mean_sd(grp1m = 95.78919, grp1sd = 6.088219, grp1n = 148,
                           grp2m = 95.79459, grp2sd = 5.826966, grp2n = 74, es.type = "d")
Soldan_PN
```

#Hassenstab
#AB-= 55.88 (4.25) 127, AB+= 56.58 (4.17) 53
#AB-=53.88 (5.21) 50, AB+=51.59 (6.38) 34
#264 (TOTAL AB-=177,AB+=87; 65-74 AB-=127, AB+=53; 75+ AB-=50, AB+=34)
```{r}
ABneg <- Calc2(127,55.88,4.25,50,53.88,5.21) # combine groups AB-

ABpos <- Calc2(53,56.58,4.17,34,51.59,6.38) # combine groups AB+
```
#ABneg  n= 177  mean= 55.31503  SD= 4.615585 
#ABpos  n= 87  mean= 54.62989  SD= 5.668369 
```{r}
Hassenstab_PN <- esc_mean_sd(grp1m = 55.31503, grp1sd = 4.615585, grp1n = 177,
                           grp2m = 54.62989, grp2sd = 5.668369, grp2n = 87, es.type = "d")
Hassenstab_PN
```

###average SD: average the variance, then sqrt(variance)
#65-74 age
#ANIMALS AB-=21.14 (5.15), AB+=21.82(4.83); 
#VEGETABLES AB-=15.05 (4.16), AB+=14.97 (4.50)
#75+ age
#ANIMALS AB-=18.31 (4.71), AB+=16.91 (3.87)
#VEGETABLES AB-=14.14 (4.08), AB+=11.96 (4.03)
```{r}
#65-74 age
#ABneg mean: 
21.14 + 15.05
#ABneg SD: 
sqrt(((5.15^2) + (4.16^2))/2)

#ABpos mean:
21.82 + 14.97
#ABposSD:  
sqrt(((4.83^2) + (4.50^2))/2)

#75+ age
#ABneg mean: 
18.31 + 14.14
#ABneg SD: 
sqrt(((4.71^2) + (4.08^2))/2)

#ABpos mean:
16.91 + 11.96
#ABposSD:  
sqrt(((3.87^2) + (4.03^2))/2)

```

#Hassenstab
#ANIMALS AB-=21.14 (5.15) 127, AB+=21.82(4.83) 53
#ANIMALS AB-=18.31 (4.71) 50, AB+=16.91 (3.87) 34
#264 (TOTAL AB-=177,AB+=87; 65-74 AB-=127, AB+=53; 75+ AB-=50, AB+=34)
```{r}
ABneg <- Calc2(127,21.14,5.15,50,18.31,4.71) # combine groups AB-

ABpos <- Calc2(53,21.82,4.83,34,16.91,3.87) # combine groups AB+
```
#ABneg  n= 177  mean= 20.34056  SD= 5.176532
#ABpos  n= 87  mean= 19.90115  SD= 5.065482 
```{r}
Hassenstab_SF <- esc_mean_sd(grp1m = 20.34056, grp1sd = 5.176532, grp1n = 177,
                           grp2m = 19.90115, grp2sd = 5.065482, grp2n = 87, es.type = "d")
Hassenstab_SF
```





